---
title: "Contrasts"
author: "Yasin Kaymaz"
date: "1/31/2019"
output:
  html_document:
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library(DT)
library(tidyverse)
source("https://raw.githubusercontent.com/yasinkaymaz/cellRtools/master/main/functions.R")
source("code/functions.R")

load("~/data/all.markers.Lake2018.FC.Rdata")
load("~/data/markers.PvalbTac1_vs_GABA.Lake2018.FC.Rdata")
load("~/data/markers.In6_vs_others.Lake2018.FC.Rdata")
load("~/data/markers.In6a_vs_others.Lake2018.FC.Rdata")
load("~/data/markers.In6b_vs_others.Lake2018.FC.Rdata")



```

Here, the purpose is to identify genes that are exclusively expressed in In6a and In6b cell population in contrast against the background cells. I considered three group of cells as background;

## Differential expression of marker genes in each of the subsets:

```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5IT.vs.Glu)))
InteractiveTable(FilterTable(allmarkers.subclass, allmarkers=T))
```

## Pvalb-Tac1 vs GABA clusters

Pvalb-Tac1 versus GABA clusters in PFC only. **Pvalb-Tac1** corresponds to In6b in Tasic2018 while **GABA clusters** are In1a, In1b, In1c, In3, In4a, In4b, In6a, In7, In8.

```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5IT.vs.Glu)))
InteractiveTable(FilterTable(markers.PvalbTac1_vs_GABA, allmarkers=F))
```

## In6 vs all others in BA10

In6 versus all remaining In groups in BA10 only. 
```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5IT.vs.Glu)))
InteractiveTable(FilterTable(markers.In6_vs_others, allmarkers=F))
```

## In6a vs all others in BA10

In6a versus all remaining In groups in BA10 only.
```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5IT.vs.Glu)))
InteractiveTable(FilterTable(markers.In6a_vs_others, allmarkers=F))
```

## In6b vs all others in BA10

In6b versus all remaining In groups in BA10 only.
```{r echo=FALSE}
#InteractiveTable(FilterTable(annotateGenes(markers.L5IT.vs.Glu)))
InteractiveTable(FilterTable(markers.In6b_vs_others, allmarkers=F))
```


.

.

.

.

.

.

